\input{hwpre.tex}

\usepackage[compact]{titlesec}

\begin{document}
\MYTITLE{Homework Assignment Two: Using Conditional Logic in Automation Tasks}
\MYHEADERS{Homework Assignment Two}{Due: September 19 and 20, 2013}

\section*{Introduction}

Tasker is described as a ``total automation system for Android'' and is often one of the reasons why people purchase
Android-based tablets and mobile phones.  You can learn more about Tasker by visiting
\url{http://tasker.dinglisch.net/}. As you will see, the creator of Tasker described it as ``an application for Android
which performs Tasks (sets of Actions) based on Contexts (application, time, date, location, event, gesture) in
user-defined Profiles, or in clickable or timer [sic] home screen widgets.''  What are some ways in which you could use
Tasker to automate the use of your tablet?

\section*{Creating Notifications in Tasker}

Take some time to explore the ``Profiles'', ``Tasks'', ``Scenes'', and ``Vars'' tabs at the top of the screen in Tasker.
Using Tasker's in-application help system and any online resources that you find, write one or two sentences about
the meaning and purpose of each tab. Now, go to the ``Tasks'' tab and use the plus sign in the bottom-right corner to
create a new task called ``Notify''.  Now, find the Notify action and customize it so that it will display a message.
Once you have completed this step, you can click the arrow in the bottom-left corner to run your task.  At this point,
you can further customize your notification task by changing the displayed message and/or the icon. 

\section*{Using Conditional Logic in Tasker}

Instead of having to load Tasker and click the run button every time you wanted to run your Notify task, it would be
better to ensure that it automatically runs when a specified condition is true.

\section*{Summary of the Required Deliverables}

To complete the assignment, you should turn in signed printouts of the: (i) list of at least five automation tasks
that you could implement in Tasker, (ii) description of the four tabs in Tasker's main screen, and (iii) .

\end{document}
