\input{hwpre.tex}

\usepackage[compact]{titlesec}

\begin{document}
\MYTITLE{Homework Assignment Eight: The Future of Mobile Apps at Allegheny College} 
\MYHEADERS{Homework Assignment Eight}{Due: December 17, 2013 by 5 pm}

\section*{Introduction}

Throughout this semester, you have learned more about mobile computing, the Android operating system, and the
fundamentals of mobile app development in both Tasker and AppInventor.  This assignment invites you to reflect on your
experiences in this group study and to partner with the instructor to further develop a vision for future instruction in
the area of mobile application development. As you complete this homework assignment, please review all of the previous
assignments that you have already completed and have been returned to you with grades and feedback.  After completing
this review, you should consider what you liked and disliked about the course and the assignments.  Finally, you should
think about how faculty members in the Department of Computer Science should teach mobile application development in
future semesters.

\section*{Envisioning the Future of Instruction on Mobile App Development}

\vspace*{-.05in}
\noindent
To complete the assignment, you should turn in a one or two page paper that responds to the following questions about
the introduction of a mobile app development course at Allegheny College: 
\vspace*{-.2in}
\begin{enumerate}
    \itemsep0em
    \item What did you like and/or dislike about the topics covered in this course?
    \item What did you like and/or dislike about the homework assignments given for this course?
    \item What additional topics would you have liked to cover during this semester?
    \item What should be the prerequisite course(s) and/or knowledge for a mobile app course? 
    \item What topics should be covered in a full course on mobile application development?  
    \item Should team-based projects continue to be a prominent part of a mobile app course?
    \item Should writing and speaking continue to be a major component of a class about mobile apps?
\end{enumerate} 

Students should individually complete this homework assignment.  You may turn in a signed and printed version of your
assignment at any point up to the stated deadline of December 17, 2013 at 5 pm. Please contact the instructor by email
if you have questions about this assignment.
\end{document}
